\documentclass[10pt,letterpaper,sans]{moderncv}

%% ModernCV themes
\moderncvstyle{classic}
\moderncvcolor{grey}
\renewcommand{\familydefault}{\sfdefault}
\nopagenumbers{}

%% Character encoding
\usepackage[utf8]{inputenc}

%% Adjust the page margins
\usepackage[scale=0.87]{geometry}

%% Personal data
\firstname{Harrison}
\familyname{Lynch}
\address{3108 Niagara Street}{Pittsburgh, PA 15213} 
\mobile{(267) 626-1225} 
\email{hal53@pitt.edu} 
\homepage{www.harrisonlynch.com} 

%%------------------------------------------------------------------------------
%% Content
%%------------------------------------------------------------------------------
\begin{document}
\makecvtitle
%\vspace*{-3em} % NEW

%\section{Objective}
%\cvitem{}{To bring my motivation and drive to Branding Brand as a Product Manager, where I can use my industrial engineering background and communication skills to deliver successful projects.}

\section{Education}
\cventry{2011-2015*\linebreak\small{*expected Dec.}}{Bachelor of Science in Industrial Engineering}{University of Pittsburgh}{Pittsburgh, PA}{}{QPA 3.74 in Major, GPA 3.803\\\emph{Minor in Mathematics}}
\cvitem{}{\textbf{Coursework: }Productivity Analysis, Materials Handling and Facilities Layout, Linear Programing and Probabilistic Operations Research, Human Factors Engineering, Design of Experiments and Quality Assurance}
\cventry{Summer 2013}{Study Abroad: Engineering for Sustainability}{Munich University of Applied Sciences}{Munich, Germany}{}{}
	\cvlistitem{Formulated a business plan for increasing sustainable tourism by repairing discarded bicycles found at train stations to be sold as rental bikes to hostels who did not offer any such services.}

\section{Experience}
\cventry{2013--2015}{Accenture Operations Workforce Optimization}{Co-op}{Pittsburgh, PA}{3 rotations}{}
	\cvlistitem{Developed and validated engineered labor standards using MOST analysis and time studies, identifying process improvement opportunities for the client.}
	\cvlistitem{Configured interfaces between a StandardsPro database and a Kronos labor forecasting system, allowing a retail client to minimize instances of under or overstaffing locations.}
	\cvlistitem{\textbf{Key Outcomes: }Delivered staffing solutions that allowed clients to maximize utilization and schedule labor based on the appropriate volume drivers and standards responsible for the work of employees.}
\cventry{Summer 2015}{Accenture Technology Vision Team}{Internship}{San Jose, CA}{}{}
	\cvlistitem{Prepared content for the 2016 Accenture Technology Vision by researching ethical issues and business implications surrounding the use of personal data in emerging technologies.}
	\cvlistitem{Communicated reasearch findings to Accenture Technology leadership on a weekly basis to receive feedback and refine focus to maximize the quality of the research efforts.}
	\cvlistitem{\textbf{Key Outcomes:} Planned and launched a collaborative research effort with 20 external stakeholders focused on the intersection of data and ethics.}
\cventry{Spring 2014}{Freshman Engineering Conference Co-Chair}{}{Pittsburgh, PA}{}{}
	\cvlistitem{Advised 6 pairs of freshman engineers on writing a research paper with topics related to sustainabile industrial engineering. Held weekly meetings with the groups to provide feedback and refine writing mechanics.}
	\cvlistitem{\textbf{Key Outcomes:} Improved freshman engineer's technical writing and presentation skills that they will need sophomore year and beyond.}

\section{Leadership}
\cventry{2013--Present}{Theta Tau - Professional Engineering Fraternity}{Brother}{}{}{}
\cvitem{}{\textbf{Brotherhood Chair, }Organized transportation to and from fraternity social events, ensuring that all brothers and pledges were provided with a safe ride.}

\section{Skills}
\cvitem{}{\textbf{Computer: }Excel, PowerPoint, Access, MiniTab, StandardsPro, R, Python, C++, Matlab, LaTeX}
\cvitem{}{\textbf{Industry: }MOST certification, Time Study certification, 5-S, Engineered Labor Standards}

\section{Organizations}
\cvitem{}{\textbf{Alpha Pi Mu} Industrial Engineering Honors Society}
\cvitem{}{\textbf{IIE} Institute of Industrial Engineers}




%\cvitemwithcomment{Language 1}{Skill level}{Comment}
%\cvdoubleitem{category X}{XXX, YYY, ZZZ}{category Y}{XXX, YYY, ZZZ}
%\cvlistitem{Item 1}
%\cvlistdoubleitem{Item 2}{Item 3}
%% ...

\bibliography{publications}
\end{document}